Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-06 paper/paper.tex
pass on V.B

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the offical
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. Table~\ref{tab:test-suites} shows the breakdown of
tests we considered. Overall, we found a total of \totfiles{} JS
files. We did not consider tests from the \chakra{} repository because
they depend on non-portable objects. Notice that the number of tests
in \veight\ is low. That happens because many tests in \veight{} are
inherited from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. The \veight{} test
suite contains other tests, but, as in \chakra{}, these tests use
non-portable testing objects that we still did not mock.

@@

This section reports results obtained with test
transplantation. Table~\ref{tab:cross-testing} shows the number of
failures that each engine produces on a different test suite. To sum,
we observed that \Fix{...}

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 6 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 279 \\
    Duktape & 0 & 4 & 4 & 1   \\
    JerryScript & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
    Tiny-js & 0 & 0 & 0 & 0  \\
    \bottomrule 
  \end{tabular}
\end{table}

>>>>

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the offical
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. Table~\ref{tab:test-suites} shows the breakdown of
tests we considered. Overall, we found a total of \totfiles{} JS
files. We did not consider tests from the \chakra{} repository because
they depend on non-portable objects. Notice that the number of tests
in \veight\ is low. That happens because many tests in \veight{} are
inherited from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. For all engines engines
we found test using non-portable functions that we detected by running
the test on a different engine. We needed to discard those.

@@

This section reports the failures observed when running a test suites
on an engine for which those tests were not run
before. Table~\ref{tab:cross-testing} shows the number of failures for
each pair of test suite and engine. The first column shows the test
suites whereas the first row shows the engines. We use a dash (``-'')
to indicate that we did not consider the combinations that associated
a test suite with the engine that originated them; failures in those
cases would either indicate regressions or flaky tests as opposed to
an unknown bug for that engine. We also discarded such test cases from
consideration in other engines as we wanted the test to pass on its
originating engine; a failure in that case would be a stronger
indicative of a bug.

To sum, we observed that, considering this dataset, the Mozilla
\smonkey\ was the engine that failed the least whereas the Microsoft
engine \chakra\ failed the most. The \smonkey\ test suite also
revealed more failures than any other, perhaps as expected,
considering that it is the suite with more tests (see
Table~\ref{tab:test-suites}). This suggests that the investiment in
testing paid off in this case.

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 6 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 279 \\
    Duktape & 0 & 4 & 4 & 1   \\
    JerryScript & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
    Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}
